---
title: "Chapter 2 Exercises"
author: "Jumping Rivers"
output: html_vignette
---
<!--
%\VignetteEngine{knitr::rmarkdown}
%\VignetteIndexEntry{Chapter 2 Exercises}
-->

```{r echo=FALSE, message=FALSE}
library("jrShiny")
library("shiny")
```

## Exercise 6 (10 minutes)

Open `chapter2/exercise6.Rmd`. This contains the answers to Exercise 5. Here we're calculating the variable `selected` twice which is inefficient.

  * Use the `reactive()` function so that the variable `selected` is only calculated once.
  
## Exercise 7 (10 minutes)

Use `chapter2/exercise6.Rmd` again.     

  * (Harder) Use an `actionButton()` and an `eventReactive()` to make it so that the plot and text only render when the button is clicked.    
  *  Change `actionButton()` to `actionLink()`    
  
## Exercise 8a (10 minutes)

Open `chapter2/exercise8.Rmd`. Here we have one button for the flower setosa and one for versicolor. We've also set up a `reactiveValues()` that initialises to the entire iris data set    
  * Use the `observeEvent()` function to update the reactiveValues to the correctly filtered data set, depending on which button the user clicks
    
## Exercise 8b

  * Convert the plot in exercise 8a to a **ggplot2** graph
  * Convert the plot from a **ggplot2** graph to a **plotly** graph
  
## Exercise 8c

  * Using `renderTable()`, add a static table of the selected data
  * Using the **DT** library, make this table an interactive table

## Exercise 9 (10 minutes)
  
  * Open `chapter2/exercise9.Rmd` and run. 
  * Include the line
    ```{r eval=FALSE}
    ## Arguments: id, code to execute on the server
    observeEvent(input$n, {print(input$n)}) 
    ```
    and look at the `R Markdown` tab. 
  * Try a different shiny widget.
  
## Exercise 10 (5 minutes)

  * Open `chapter2/exercise10a.Rmd` and run. 
    * Add a second slider and display the sum of both sliders.
    * Let the slider determine the value of `n` in an `rnorm` call, i.e. `rnorm(input$n)`.
    * Using `renderPlot()`, generate a scatter plot of random numbers where the sample size is determined by a slider.
  * Open `chapter2/exercise10b.Rmd` and run. 
    * Create another `sliderInput()` widget to control the mean value used in the `rnorm()` function call, i.e.
        ```{r eval=FALSE}
        ## input$mean comes from a second slider
        rnorm(input$n, input$mean)
        ```
    * Add in a `selectInput()` widget to switch between generating random numbers from 
    a normal distribution and a uniform distribution. For a uniform distribution you would use the `runif()` function.  
    * Add `renderText(input$n)` to the script to print the value  of `input$n`.
    * Instead of printing `input$n`, print out the largest value in the sample.
        * Do you see a problem?

## Exercise 11

  * Open `chapter2/exercise11.Rmd` and run. 
  * Fix the syncing problem between the plot and the text by using the `reactive()` function.
  * Add in a `selectInput()` widget to switch between generating random numbers from a normal distribution
  and a uniform distribution.
    
## Exercise 12

  * Open `chapter2/exercise12.Rmd` and run. 
  * Using `eventReactive()`, only redraw the graph and calculate the maximum value when the `Plot it` button is pressed.
  * Change `actionButton()` to `actionLink()`

## Exercise 13

  * Open `chapter2/exercise13.Rmd` and run. 
  * Using `reactiveValues()` and `observeEvent()` to only redraw the plot when a button is clicked.

----

## Further Reading

When I was developing this tutorial, I created a couple of simple examples to illustrate different shiny components. These examples are found in `chapter2/` and the files start with `Why_`.










<!-- ## Exercise 1 -->

<!-- Copy the [simple_shiny](simple_shiny.Rmd) file to RStudio and knit.  -->

<!-- 1. The `sliderInput` functions control the year selection. Change the `min`, `max`, `step` and `value` arguments. -->
<!-- 1. The `selectInput` function highlights the points. Look at the `colnames(movies)` and add -->
<!-- a few more options. -->
<!-- 1. The first arguments of `sliderInput` and `selectInput` are unique ids. Look at the plotting code -->
<!-- and see how they interact. -->
<!-- 1. Add another `sliderInput` that controls the maximum value to display on the `y`-axis.  -->

<!-- ## Exercise 2 -->

<!-- Re-copy the [simple_shiny](simple_shiny.Rmd) file to RStudio. -->

<!--  * Run  -->
<!--     ```{r results="hide"} -->
<!--     sliderInput("min_year", label = "Minimum year:", min=1930, max=2010, step=10, value=1930, sep="") -->
<!--     ``` -->
<!--     in your console and examine the output. Try changing `min` and `max`. Re examine the output. -->

<!--   * Go to the shiny widgets [gallery](http://shiny.rstudio.com/gallery/widget-gallery.html) and -->
<!--   experiment with a few of the widgets. -->
<!--   * Change the `selectInput` widget to `radioButtons`. Hint: Look at the example in the `radioButton` help page -->

<!-- ## Exercise 3 -->

<!-- Re-copy the [simple_shiny](simple_shiny.Rmd) file to RStudio. -->

<!--   * Open the [shiny components](shiny_components.Rmd) and knit -->
<!--   * Change the scatter plot in the shiny app, to a histogram that displays movie `Rating`.  -->
<!--   The drop-down menu should now select the type of movies displayed, e.g.  -->
<!--   if `Action` is selected, only `Action` movies as displayed in the histogram. -->

<!--   * Create another pane in the shiny app. Use `renderText` to display the total number of movies in the histogram. -->
<!--   * __Harder__: Add an interactive [value boxes]{http://rmarkdown.rstudio.com/flexdashboard/using.html#value_boxes}. Select -->
<!--   a suitable icon from [ionicons](http://ionicons.com/) -->


<!-- ### Further examples -->

<!--  * [Biclust](https://jjallaire.shinyapps.io/shiny-biclust/) -->
<!--  * [crandash](https://jjallaire.shinyapps.io/shiny-crandash/) -->
<!--  * [Brushing](https://jjallaire.shinyapps.io/shiny-ggplot2-brushing/) -->
<!--  * [kmeans](https://jjallaire.shinyapps.io/shiny-kmeans/) -->
<!--  * [diamonds](https://jjallaire.shinyapps.io/shiny-ggplot2-diamonds/) -->


<!-- ## Exercise 4 -->

<!--   * Add the drop down menu button -->
<!--   ```{r results="hide"} -->
<!--   selectInput("mpaa", label = "MPAA", c("R", "PG-13", "PG", "NC-17")) -->
<!--   ``` -->
<!--   to the side bar. When a mpaa rating is changed, the plots should be updated. -->
<!--   * Include an additional term  - `all` - to indicate that all ratings should be displayed. -->

<!-- ## Exercise 5 -->

<!--   * Update the other pages of the [shiny components](shiny_components.Rmd) file to use \cc{reactive}  -->
<!--   expressions. -->

<!-- ## Exercise 6 -->

<!--   * Make pages 2 & 3 of the [shiny components](shiny_components_reactive_isolate.Rmd) use `isolate`. -->



