---
title: "Chapter 2 Exercises"
author: "Jumping Rivers"
output: html_vignette
---
<!--
%\VignetteEngine{knitr::rmarkdown}
%\VignetteIndexEntry{Chapter 2 Exercises}
-->

```{r echo=FALSE, message=FALSE}
library("nclRshiny")
library("flexdashboard")
```

## Exercise 1 (5 minutes)

  * Briefly explore the [showcase](http://www.htmlwidgets.org/showcase_leaflet.html) htmlwidgets. 
  * I've also deploy a simple [app](https://bookdown.org/csgillespie/components/) This is what we
  hope to achieve by the end of chapter 3.

## Exercise 2 (20 minutes)

Go through the following widgets

  * Interactive Heat Maps: [d3heatmap](d3heatmap.html), [R](d3heatmap.R), [Rmd](d3heatmap.Rmd)
  * Interactive tables: [DT](DT.html), [R](DT.R), [Rmd](DT.Rmd)
  * Circle Plots with Bundled Edges: [edgebundleR](edgebundleR.html), [R](edgebundleR.R), [Rmd](edgebundleR.Rmd)
  * Formattable Data Structures: [formattable](formattable.html), [R](formattable.R), [Rmd](formattable.Rmd)
  * Interactive ggplot2 graphs: [ggiraph](ggiraph.html), [R](ggiraph.R), [Rmd](ggiraph.Rmd)
  * Network graphs: [networkD3](networkD3.html), [R](networkD3.R), [Rmd](networkD3.Rmd)
  * Add pan and zoom to graphics: [svgPanZoom](svgPanZoom.html), [R](svgPanZoom.R), [Rmd](svgPanZoom.Rmd)
  * jQuery Sparkline HTML Widget: [sparkline](sparkline.html), [R](sparkline.R), [Rmd](sparkline.Rmd)

Experiment with a few of the widgets on your **own** data set.

## Exercise 3 (20 minutes)

Open the `htmlwidgets` vignette

```{r eval=FALSE}
vignette("htmlwidgets", package="nclRshiny")
```

Explore the **other widgets** on you own data. The `plotly` framework, under _Entire plotting frameworks_ is quite nice

## Exercise 4 (10 minutes)

Create:

  * A markdown document containing your widgets;
  * A markdown presentation containing your widgets.
  
  
  
