---
title: "Introduction to edgebundleR"
date: "`r Sys.Date()`"
author: "Jumping Rivers"
output: html_vignette  
---
<!--
%\VignetteEngine{knitr::rmarkdown}
%\VignetteIndexEntry{Introduction to edgebundleR}
-->
  
```{r message=FALSE, echo=FALSE}
library("edgebundleR")
```

## Overview

This package creates a hierarchical edge bundle plots; similar to the D3 [example](http://bl.ocks.org/mbostock/7607999). The main function in the package is `edgebundle()`. It takes in a variety of inputs:

  * an [igraph](https://cran.r-project.org/web/packages/igraph/index.html) object
  * a symmetric matrix, e.g. a correlation matrix or (regularised) precision matrix
  * a JSON file structured with name and imports as the keys

You can install this (large) package using 

```{r, eval=FALSE}
install.packages("edgebundleR")
```

## Examples 

```{r, echo=FALSE, message=FALSE}
library(edgebundleR)
library(MASS)
data(mtcars, package="datasets")
sig = kronecker(diag(3),matrix(2,5,5)) + 3*diag(15)
X = MASS::mvrnorm(n=100,mu=rep(0,15),Sigma = sig)
colnames(X) = paste(rep(c("A.A","B.B","C.C"),each=5),1:5,sep="")
edgebundle(cor(X),cutoff=0.2,tension=0.8,fontsize = 14)
```

It can also be used for displaying correlation matrices. We simply calculate the correlation and set 
any correlations between $-0.7$ and $0.7$ to be zero
```{r, message=FALSE}
cor_mt = cor(mtcars)
cor_mt[cor_mt < 0.7 & cor_mt > -0.7] = 0
```
Then plot as usual
```{r}
edgebundle(cor_mt)
```

#### Further information

  * [github](https://github.com/garthtarr/edgebundleR)
