---
title: "Introduction to ggiraph"
date: "`r Sys.Date()`"
author: "Jumping Rivers"
output: html_vignette  
---
<!--
%\VignetteEngine{knitr::rmarkdown}
%\VignetteIndexEntry{Introduction to ggiraph}
-->
  
```{r message=FALSE, echo=FALSE}
library("ggiraph")
gg_th <- theme(axis.ticks = element_line(colour = "gray90"), 
    panel.grid.major = element_line(colour = "gray90"), 
    panel.grid.minor = element_line(colour = "transparent"), 
    panel.background = element_rect(fill = "transparent"))

```

## Overview

The `ggiraph` attempts to produce interactive ggplot2 graphics. It extends `ggplot2` with new geom functions:

  * `geom_point_interactive`
  * `geom_polygon_interactive`
  * `geom_map_interactive`
  * `geom_path_interactive`
  * `geom_rect_interactive`
  * `geom_segment_interactive`
  * `geom_text_interactive`

You can install the package via

```{r eval=FALSE}
install.packages("ggiraph")
```

## Example: Clickable links

Perhaps the most interesting feature is that you can add links to points

```{r echo=FALSE}
data(USArrests, package="datasets")
crimes <- data.frame(state = tolower(rownames(USArrests)), USArrests)
crimes$onclick <- sprintf(
  "window.open(\"%s%s\")",
  "http://en.wikipedia.org/wiki/",
  as.character(crimes$state)
)

gg_point_3 <- ggplot(crimes, aes(x = Murder, y = Assault, size = UrbanPop, colour = Rape )) + 
  geom_point_interactive(
    aes( data_id = state, tooltip = state, onclick = onclick ) ) + 
  scale_colour_gradient(low = "#999999", high = "#FF3333") + gg_th

ggiraph(code = print(gg_point_3), 
        hover_css = "fill-opacity:.3;cursor:pointer;")
```
#### Links

  * [CRAN](https://cran.rstudio.com/web/packages/ggiraph/)
  * [github](https://github.com/davidgohel/ggiraph/)
  