---
title: "Chapter 3 Exercises"
date: "`r Sys.Date()`"
author: "Jumping Rivers"
output: html_vignette
---
<!--
%\VignetteEngine{knitr::rmarkdown}
%\VignetteIndexEntry{Chapter 3 Exercises}
-->

## Exercise 14

  * Open `chapter2/exercise14.R ` and run.
  * Create a new directory, with two files: `ui.R` and `server.R`
    * Move the ui section of the app to `ui.R` 
    * Move the server section of the app to `server.R`
    * Rerun the app via these new files.
  * Change the scatter plot to a histogram of movie lengths. If you're not comfortable with **ggplot2**, feel free to do it in base.
  
## Exercise 15

  * Open `chapter2/exercise15.R` and run. Experiment with the columns widths.
    * You can move columns to the right by adding the `offset` parameter to the `column()` function, e.g. ` column(4, offset=1, ...)`
  * Reproduce
    
    ```{r echo=FALSE, message=FALSE, fig.height=4, fig.width=4}
    library(jrShiny)
    layout(matrix(c(1, 1, 1, 0, 2, 0), 2, 3, byrow = TRUE), heights = c(8, 4))
    layout_show(2, text = c("Plot", "Drop down"))
    ```
    
    Hint: You will need to use the `offset` argument

  * Reproduce
  
    ```{r echo=FALSE, message=FALSE, fig.height=4, fig.width=4}
    library("jrShiny")
    layout(matrix(c(0, 1, 1, 1, 1, 1, 0,
                    0, 0, 2, 2, 2, 0, 0), 2, 7, byrow = T), heights = c(8, 4))
    layout_show(2, text = c("Plot", "Drop down"))
    ```
    
    Hint: You will need to use the `offset` argument and two `fluidRow`

## Exercise 16

  * In RStudio, select `File`, then `New File`, then `Shiny Web App`
  * Create an appropriate app name, and make sure you select to split it into `ui.R/server.R`
Congrats, you've just created your first shiny app! We're going to use the iris data set to build up a shiny app.
  * In the UI, remove the `sliderInput()` from the siderbarPanel and add the `selectInput()` from exercise 5, i.e.
    ```{r, eval = FALSE}
    selectInput("flower_choice", "Choose your flower",
                choices = unique(iris$Species))
    ```
  * Change the ID of the plotOutput to something more appropriate for the iris data set.
  * In `server.R`, get the plot to display the plot from exercise 6
    
<!-- ## Exercise 3: Layouts -->

<!--   * Open `chapter2/layout_app1.R` and run. -->
<!--   * Add a new tab to the output -->
<!--     * Let this new tab show a table of two variables, `length` and `rating`. -->
<!--     * Try making this an interactive table using `DT::datatable`. -->
<!--     * Make sure to remember to use the right `render*` and `*Output` functions. -->

<!-- A second exerise using the `navbarPage` function -->

<!--   * Open `chapter2/layout_app2.R` and run -->
<!--   * Add a new page to the output -->
<!--     * Let this new tab show a table of two variables, `length` and `rating`. -->
<!--     * Try making this an interactive table using `DT::datatable`. -->
<!--   * Try using `navbarMenu` to create a dropdown menu that combines both the summary page and your new tab. -->
<!--   * If you wanted you could also try to create something that allows different input data to be shown within each tab -->

<!-- ## Exercise 4: Dashboards -->

<!--   * Open `chapter2/dashboard_app1.R` and run. -->
<!--   * The app currently shows a list of available functions from the `shinydashboard` package. -->
<!--   * Use the available functions to create a new tab which plots `length` against `rating` for the `movies` data. -->
<!--   * Add a value box that shows the number of movies that are longer than 4 hours. -->
<!--   * Experiment with changing icons for your tabs and boxes. -->

<!-- ## Exercise 5: interactive graphics -->

<!--   * Open `chapter2/interactive1.R` and run. -->
<!--     * Change the output to display `x` and `y` to 4 significant figures. -->
<!--     * If you are familiar with `ggplot2`, change the base graphic plot to a ggplot2 scatter plot.  -->
<!--     * Change the plot to a boxplot - does it still work -->
<!--   * Open `chapter2/interactive2.R` and run. Explore the other types of point selection. -->

<!-- ## Exercise 6: acting on interactive graphics -->

<!--   * Open `chapter2/interactive3.R` and run. -->
<!--   * In the `nearPoints` function, what does -->
<!--     * the argument `maxpoints=1` do? -->
<!--     * the argument `allRows=TRUE` do? -->
<!--   * On the scatter plot, add a line of best fit using the `lm` function -->
<!--     * When you click on a point, remove that point from the regression calculation and -->
<!--     refit the line. -->
<!--     * Add a reset button to you app -->
<!--     * Rather than clicking on a point, try brushing - selecting multiple, and altering the line. -->

<!-- ## Exercise 7: invalidating reactive contexts -->

<!--   * Open `chapter2/invalidate.R` and  run. -->
<!--   * Can you change the app such that it produces a plot of movie ratings vs lengths from a random sample of movies that changes every 5 seconds -->
<!--   * Create a summary output of movie years, let this be it's own reactive context updating every 3 seconds from a random sample of movies. -->
<!--   * __Hard:__ Create a summary output of movie years, let this be it's own reactive context updating every 3 seconds by cycling through the movie genres. -->
