---
title: "Chapter 3: Layouts"
author: "Jumping Rivers"
date: "`r Sys.Date()`"
#output: revealjs::revealjs_presentation
output: ioslides_presentation
css: left.css
---
<!--
%\VignetteEngine{knitr::rmarkdown}
%\VignetteIndexEntry{Chapter 3 Slides}
-->

## flexdashboard: Dashboard creation

  * Provides a format for converting R markdown into a grid oriented dashboard
  * Adapts size of components to the containing web page

## flexdashboard: Dashboard creation

  * Interactive JavaScript data visualisations based on htmlwidgets.
  * R graphical output including base, lattice, and grid graphics.
  * Tabular data (with optional sorting, filtering, and paging).
  * Value boxes for highlighting important summary data.
  * Gauges for displaying values on a meter within a specified range
  * Text annotations of various kinds.

# Layouts
## Layouts

The `flexdashboard` package makes it easy to create dashboards. 
  
   * Single column (fill and scrolling);
   * Rows;
   * Multiple columns;
   * Tabs;
   * Pages.
  
New chart panes are created using `###` and new columns (or
  rows) are created using `------------------`

## flexdashboard: demo single column (fill)

# Exercise 1
## Exercise 1

```{r eval=FALSE}
vignette("chapter3", package="nclRshiny")
```

# Sizing
## Sizing
  
 * We can also change the sizes of dashboard panes.
 * If no size  attributes are specified then each chart size is relative to it's
    `knitr` figure size (576 by 460 pixels)
 * To specify the size, we use the `data-width` and `data-height` attributes to rows, columns, or even individual
    charts.
  * These attributes establish the _relative_ size
    between charts laid out in the same dimension.

# Exercise 2
## Exercise 2

```{r eval=FALSE}
vignette("chapter3", package="nclRshiny")
```

# Appearance
## Appearance
  
  * You can alter the overall theme of the dashboard by add a theme element in the header.
  * You can also add [bespoke](http://rmarkdown.rstudio.com/flexdashboard/using.html#appearance) `css` code, logos and favicon's.


