---
title: "Sparklines"
author: "Jumping Rivers"
css: "sparkline.css"
output: html_vignette
---
<!--
%\VignetteEngine{knitr::rmarkdown}
%\VignetteIndexEntry{Introduction to Sparklines}
-->  

```{r echo=FALSE}
library("htmlwidgets")
library("sparkline")
set.seed(3)
x = signif(rnorm(10), 2)
y = signif(rnorm(10), 2)
```

A sparkline is a very small line chart `r sparkline(cumsum(x))`. They are typically drawn without axes or coordinates.
The graph presents the general shape of the variation (typically over time) in some
measurement: `r sparkline(x, type = 'bar')`.  Sparklines are small enough to be
embedded in text  `r sparkline(abs(x), type = 'bar')`. They are often included within tables

Bar charts   negative values: 

| Object | Sparkline         | Boxplot  
|-------|-------------------|--------
| `x`     | `r sparkline(x)`  | `r sparkline(x, type ='box')`
| `y`     | `r sparkline(y)`  | `r sparkline(y, type ='box')`


You can install the developmental version using

```{r eval=FALSE}
devtools::install_github("htmlwidgets/sparkline")
```

#### Further information

 * Experimental R [package](https://github.com/htmlwidgets/sparkline)
 * javascript [library](http://omnipotent.net/jquery.sparkline/)
 * [Wikipedia](https://en.wikipedia.org/wiki/Sparkline) page